\section{Policy on Revisions of Data and Code Deposits in the AEA Data and Code Repository}\label{policy-on-revisions-of-data-and-code-deposits-in-the-aea-data-and-code-repository}

Once an article has been published in an AEA journal, the associated
data and code deposit will also have been published in the
\urlcite{https://www.openicpsr.org/openicpsr/search/aea/studies}{AEA Data
and Code Repository}. Both publications are considered permanent.

However, it may become necessary or desirable to update the code and
data deposit associated with a published manuscript.%
\footnote{Also available on the web at \url{https://www.aeaweb.org/journals/data/policy-revisions}.} 
Reasons may
include:

\begin{itemize}
\tightlist
\item
  the code or the data have been updated to more accurately or more
  easily reproduce the results in the manuscript
\item
  data which previously could not be made available is now
  redistributable
\item
  the data availability has changed and the availability statement
  should be updated
\item
  the data are found to contain confidential or copyrighted materials
\end{itemize}

\subsection{Policy}\label{policy}

\subsubsection{No Replacement}\label{no-replacement}

All previously published deposits will remain available, except when
privacy or copyright infringements have been identified. When updating
and publishing a deposit, a new version is created (V1, V2, etc.). All
versions connect to each other, for example, if a V2 has been created,
there is an indication from the V1 version that it exists, and vice
versa.

\subsubsection{Infringement}\label{infringement}

Should a data and code deposit be found to be in infringement of
copyright, confidentiality, or other data use agreements, it may be
``unpublished.'' The repository will continue to display metadata,
including filenames, but the files will no longer be available.

\subsubsection{Identifying That the Deposit Has Been
Updated}\label{identifying-that-the-deposit-has-been-updated}

All data and code deposits are required to have a README. For updates,
the README should clearly state (within the first paragraph or as a
banner) that it was updated after publication.

Suggested language:

\begin{quote}
The data and code in this deposit have been updated after publication of
the article. For changes made, see below.
\end{quote}

After an introductory paragraph, a clearly identified section or
paragraph called ``Changes Made'' should also be added. This should
briefly and succinctly describe the changes made.

Examples:

\begin{quote}
The code has been simplified, and better instructions provided. All
results are the same.
\end{quote}

\begin{quote}
Permission was obtained by the data provider to post additional data.
Figures 5, 8, and 10 are now reproducible with this archive.
\end{quote}

\subsubsection{Minimal Modifications}\label{minimal-modifications}

Authors should update only those files that need to be added, edited, or
removed. Wholesale replacement of the entire archive is not allowed.

\subsubsection{Review and Approval}\label{review-and-approval}

In all cases, the AEA Data Editor will need to review the updated
materials provided.

The AEA Data Editor will review the metadata associated with the new
version. However, the same level of verification of computational
reproducibility afforded to new submissions cannot be provided, except
in select cases.

\subsubsection{Version of Record and
Linking}\label{version-of-record-and-linking}

When the article is published, the approved version of the data and code
deposit becomes the version of record. In the case of a minimal update,
the AEA will consider the updated version as the new version of record
and will change the link from the article page to point to that
version.~ For any substantive updates, the link will not be changed.~
However, in all cases, all published versions of the data deposit will
be visible on the repository page.

Minimal changes include:

\begin{itemize}
\tightlist
\item
  clarity of documentation in README or code
\item
  ­modifications to the deposit that do not affect the computation of
  the tables and figures in the manuscript
\end{itemize}

Substantive changes include:

\begin{itemize}
\tightlist
\item
  new data or code, even if it improves the overall reproducibility of
  the package
\item
  any modification to data or code that has the potential to change
  tables and figures
\end{itemize}

\subsection{Practical
Considerations}\label{practical-considerations}

\subsubsection{Prerequisites: Deposit
Ownership}\label{prerequisites-deposit-ownership}

If the materials were deposited with the AEA prior to the
announcement
of the 2019
Data and Code Availability Policy \citep{10.1257/pandp.110.dcap}, the ``owner'' of the deposit is the
AEA Data Editor. In order to update the deposit, authors should request
that the AEA Data Editor share the deposit with them.

If the deposit was made after July 2019, one of the authors retains the
ability to submit revisions.

\subsubsection{Uploading Changes}\label{uploading-changes}

When uploading changes, authors should consult the generic
\urlcite{https://www.openicpsr.org/openicpsr/aea/deposit-instructions}{AEA
Deposit Instructions} and
\urlcite{https://aeadataeditor.github.io/aea-de-guidance/data-deposit-aea.html}{supplementary
guidance}. In particular, we encourage authors to update and enrich any
metadata previously not entered, such as geographic scope and time
periods covered by the data.

\begin{itemize}
\tightlist
\item
  If replacing files, you will first need to delete the original file.
\item
  Do not replace anything that does not need replacing (in other words,
  use surgical replacement rather than bulldozer replacement).
\item
  Do not upload ZIP files. All files need to be expanded. You may use
  the "Import from ZIP" functionality.
\end{itemize}

\subsubsection{Publishing Changes}\label{publishing-changes}

When publishing a deposit, a new version number is automatically
assigned. A title for that version can be provided. Suggested version
titles:

\begin{itemize}
\tightlist
\item
  Post-publication update fixing various issues
\item
  Post-publication update providing additional data
\end{itemize}
