\section{Policy for Papers Conducting Experiments and Collecting Primary  Data}\label{policy-for-papers-conducting-experiments-and-collecting-primary-data}

For experimental papers and papers that collect primary data via
surveys, additional rules apply.%
\footnote{Also available on the web at 
	\url{https://www.aeaweb.org/journals/data/policy-experimental}.}
We normally expect authors of such
articles to supply the following supplementary materials, in addition to
the materials required by the standard \hyperref[data-and-code-availability-policy]{Data and Code
Availability Policy}. Any exceptions to this policy should be requested
at the time of submission.

\subsection{Original Instructions}\label{original-instructions}

The original instructions for the experiment or survey should be
summarized in the submitted manuscript as part of the discussion of the
experimental or survey design and should be provided in full as an
appendix at the time of submission. Instructions should convey the
protocol clearly enough that the design could be replicated by a
reasonably skilled experimentalist or survey specialist.

\subsection{Subject Selection}\label{subject-selection}

Information about subject eligibility or selection, such as exclusions
based on past participation in experiments, college major, demographic
characteristics, etc., should be summarized as part of the discussion of
design in the submitted manuscript.

\subsection{Software and Scripts}\label{software-and-scripts}

Any computer programs, configuration files, or scripts used to run the
experiment or develop the survey instrument, e.g.,
\urlcite{https://www.ztree.uzh.ch/en.html}{z-Tree} code,
\urlcite{https://www.qualtrics.com/support/survey-platform/survey-module/survey-tools/import-and-export-surveys/}{Qualtrics},
and \urlcite{https://www.limesurvey.org/}{LimeSurvey}, shall be provided.
These should be summarized as appropriate in the submitted manuscript
and deposited in the \urlcite{https://www.openicpsr.org/openicpsr/aea}{AEA
Data and Code Repository}. All requirements noted in the
\hyperref[data-and-code-availability-policy]{AEA Data and Code Availability Policy} for programs
apply.

Where appropriate, human-readable versions of the experiment or
instrument (PDF of questionnaire) shall also be provided.

\subsection{Raw Data}\label{raw-data}

The raw data from the experiment or survey should be summarized as
appropriate in the submitted manuscript and deposited in the AEA Data
and Code Repository, compliant with any confidentiality protections that
apply.

We strongly suggest that the deposit separates the raw data and
instructions from other replication materials, in order to provide
greater visibility to the author's work.

\subsection{Analysis Programs}\label{analysis-programs}

All requirements for final and intermediate data files, as well as
cleaning and analysis programs, as per the general
\hyperref[data-and-code-availability-policy]{Data and Code Availability Policy}, continue to
apply.
